---
title: "Coronavirus"
author: "Thanusaa Kanagasingam"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      countIncrementalSlides: no
      highlightLines: yes
      highlightStyle: github
---

```{r, echo = F, message = F, warning = F, fig.align='center'}
  library(tidyverse)
  library(coronavirus)
  library(kableExtra)
  knitr::opts_chunk$set(fig.width = 10, fig.height = 5, fig.align = 'center')
```

# Dataset: Coronavirus

Due to the current situation, I would like to look at the Coronavirus dataset.

Firstly, we follow the following steps:
* load package and save data in a variable
* filter data by **confirmed cases**


```{r, eval = FALSE, include = TRUE, message = FALSE, warning = FALSE}
library(coronavirus)
library(tidyverse)

dat <- coronavirus
dat <- dat %>% 
  filter(type == "confirmed")
```


???
* Daily summary of the Coronavirus (COVID-19) cases by state/province.
* The dataset contains the daily summary of Coronavirus cases (confirmed, death, and recovered), by state/province.

---
class:middle

# Confirmed cases

We look at the top 10 confirmed cases by state:

```{r, eval = FALSE, include = TRUE, message = FALSE, warning = FALSE}
coronavirus %>%
  filter(type == "confirmed") %>%
  group_by(country) %>%
  summarise(total = sum(cases)) %>%
  arrange(-total) %>%
  head(10) 
```

---

```{r, eval = TRUE, include = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
dat <- coronavirus %>%
  filter(type == "confirmed") %>%
  group_by(country) %>%
  summarise(total = sum(cases)) %>%
  arrange(-total) %>%
  head(10)  

dat %>%
  knitr::kable() %>% 
  row_spec(1, background = "yellow") %>%
  row_spec(2, background = "yellow") 
```

---

# Cases in Germany

In the following plot, you can see the COVID-Cases in Germany: 

```{r, eval = F}
dat <- coronavirus  %>% 
  filter(country == "Germany")

ggplot(data = dat, aes(as.Date(date, "%m.%d"), cases)) +
  geom_col(fill = 'firebrick') +
  scale_x_date(date_labels = "%Y/%m/%d") +
  xlab("date") + 
  ylab("cases") +
  ggtitle("Cases in Germany")
```

---

```{r, echo = F}
dat <- coronavirus  %>% 
  filter(country == "Germany")

ggplot(data = dat, aes(as.Date(date, "%m.%d"), cases)) +
  geom_col(fill = 'firebrick') +
  scale_x_date(date_labels = "%Y/%m/%d") +
  xlab("date") + 
  ylab("cases") +
  ggtitle("Cases in Germany")
```





